%-------------------------
% Resume in Latex
% Author : Aditya Godse
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage[version=4]{mhchem}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.50in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\customList}[2]{%
  \begin{itemize}[leftmargin=0.15in, label={}, itemsep=#1, parsep=#2]
    \small
    #2
  \end{itemize}%
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}


% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{center}
  \textbf{\Huge \scshape Aditya Godse} \\ \vspace{8pt}
  \small 
  \faIcon{github} \href{https://github.com/adimail}{\underline{\textcolor{blue}{github.com/adimail}}} $  $
  \faIcon{globe} \href{https://adimail.github.io/}{\underline{\textcolor{blue}{adimail.github.io}}} $  $
  \faIcon{linkedin} \href{https://www.linkedin.com/in/adimail2404/}{\underline{\textcolor{blue}{linkedin/adimail2404}}} $  $
  \faIcon{envelope} \href{mailto:adimail2404@gmail.com}{\underline{\textcolor{blue}{adimail2404@gmail.com}}}
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AISSMS Institute of Information Technology}{June 2026}
      {Bachelor of Technology in Artificial Intelligence and Data Science}{CGPA: 7.72/10, Pune, India}
    \resumeItemListStart
      \resumeItem{Major Course:}{DevOps}
      \resumeItem{Minor Course:}{Instrumentation Engineering}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


% -------------------- SKILLS --------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item \textbf{Languages}{: C/C++, Python, JavaScript, TypeScript, Ruby, Go, Astro} \\
        \item \textbf{Tools}{: Git/GitHub, Github Actions, CI/CD pipelines, GraphQL, Docker, Shell scripts,  beautifulsoup, react-native, AWS CLoud, NextJS, ESLint, Tensorflow, Pytorch, OpenCV, Webpack}
        \\
    }
\end{itemize}

% -------------------- PROJECTS --------------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://www.npmjs.com/package/hosteze-icons}{\textbf{hosteze-icons (npm package)}} $|$ \footnotesize\emph{TypeScript, Webpack, npm}}{July. 2024}
\resumeItemListStart
    \resumeItem{Built an internal tool to distribute SVG icons used on the web and mobile applications of hosteze.in}
    \resumeItem{Built a lightweight bundle using Webpack \hfill \href{https://adimail.github.io/hosteze-icons/}{\textit{Documentation} \footnotesize{\faIcon{globe}}}}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://adimail.github.io/posts/telegram-scrapping/}{\textbf{CRM Tool (ETL pipeline)}} $|$ \footnotesize\emph{Astro, supabase, AWS S3, Python, aisensy}}{May. 2024}
\resumeItemListStart
    \resumeItem{ETL pipeline to extract data from multiple sources, transform it to meet business requirements, and load it into a centralized data warehouse on S3. Developed a system for customer communication via whatsapp.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://mermaid-mind.vercel.app/}{\textbf{Mermaid Mind (Web/LLM)}} $|$ \footnotesize\emph{Monaco Editor, LLM, Gemini, Next.js, MongoDB, NextAuth, tRCP, }}{May. 2024}
\resumeItemListStart
    \resumeItem{Web application to generate Mermaid diagrams using natural language with gemini-1.5-pro base model.}
    \resumeItem{Used tCRP for server actions and Zustand for state management.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/adimail/moneyball-native}{\textbf{Moneyball (Android/IOS/Web)}} $|$ \footnotesize\emph{React Native, JavaScript, Firebase, Google Cloud, Mobile Development}}{Feb. 2024}
\resumeItemListStart
    \resumeItem{Cross-platform application to manage financial history with Firebase as a backend, optimizing performance using best NoSQL practices.}
    \resumeItem{Hosted a website and built an Android application from a single source code}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/adimail/torrent-client}{\textbf{bittorrent client (CLI Tool)}} $|$ \footnotesize\emph{Go, Concurrency patterns, Bittorrent, Unit Testing, Bencoding}}{Jan. 2024}
\resumeItemListStart
    \resumeItem{Build a lightweight software application designed to download large files using the BitTorrent protocol.}
    \resumeItem{A peer-to-peer (P2P) communication protocol used for distributing large amounts of data over the internet.}
    \resumeItem{Learnt an efficient way to structure Go projects}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://adimail.github.io/visual-data-structures/}{\textbf{Visual Code Studio (Web)}} $|$ \footnotesize\emph{TypeScript, React}}{Dec. 2023}
\resumeItemListStart
    \resumeItem{DSA and pathfinding algorithms simulator.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/adimail/Webscrapping_watershed_pune_district}{\textbf{Maharashtra watershed web scrapper (python)}} $|$ \footnotesize\emph{python, Beautiful Soup}}{Nov. 2023}
\resumeItemListStart
    \resumeItem{Collaborated on a research project with college faculty, extracting watershed information in Maharashtra through web scraping the government site.}
    \resumeItem{Utilized the gathered data for the validation of a QGIS model.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{Chief Technology Officer, Hosteze (Startup)} $|$ \footnotesize\emph{AWS, System Design, GraphQL}}{Feb. 2024 - Present}
        \begin{itemize}
        \item Responsible for the design, development, testing, and maintenance of the core product, while also maintaining a comprehensive technical documentation for the codebase.
        \item Built an internal analytical CRM tool that analyzes customer data via an ETL data pipeline to study housing market in Pune and improve our reach.
        \item Optimized the development workflow using CI/CD pipelines, creating a maintainable and robust application architecture that enhances usability and improves code readability and developer experience.
        \end{itemize}

    \resumeSubHeadingListEnd 
    
\section{Other Achivements}
        \begin{itemize}
            \item Title Holder for Asia's Largest Painting on Recycled Paper Canvas \hfill (Aug. 2021)
            \item Scientist of the Year Award in highschool for Active Participation in Science Fairs \hfill (Feb. 2019)
            \item 2 times National Level Rope Skipping Gold Medalist (Doube unders \& Spot jump) \hfill (2016 - 2017)
        \end{itemize}

\end{document}